Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-20 article.tex
remove unfinish sentence
wording

From the pre-processing to the weighted averaging of partial correlation
matrix, all pre-processing and post-processing is useful to improve score

\begin{figure}[bth]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaging method, partial correlation used filter $f_1$).}
\label{fig:curves}
\end{figure}

>>>>

\begin{figure}[bth]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaged partial correlation method, partial correlation used
         filter $f_1$).}
\label{fig:curves}
\end{figure}
